A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Conclude

\paragraph{Future work} We could create a hybrid algorithm. This would use \McSplit\ near the top of the search tree, switching to a
clique encoding when fewer than some threshold number of vertices remain to be
selected. This might deliver the benefits of the clique encoding for
labelled graphs, while avoiding the high memory cost and colouring time of
encoding the full instance.

We have yet to fully investigate variable and value ordering heuristics, i.e.\ the selection of a label class and the selection of a vertex from that label class.
There is also the potential to branch on both sides, that is instead of branching on vertices in $\V(G)$, it would be equally valid to branch on
a vertex in $\V(H)$, since our data structure treats the
two graphs symmetrically. More interestingly, we could choose which graph to branch on
at each search node using some heuristic (perhaps choosing based on whether the $P$ or
$T$ set is smaller), so long as we can ensure that the search remains complete.

We have not yet explored parallel versions of the algorithm. The first paralellism is \emph{within-core}, using bitsets to encode sets. The second parallelism  is  multithreaded,
exploited the ubiquitous multicore architecture.

? Portfolio algorithms---finding out at what level of labelledness clique becomes best etc.

%Application to induced subgraph isomorphism (with almost no changes). Applications
%of a similar technique to other problems???

>>>>

To further improve the state of the art, we could try creating a hybrid
algorithm.  This could use $k\downarrow$ initially, switching to \McSplit\ when
the extra filtering is ineffective, and finally switching to a clique encoding
when fewer than some threshold number of vertices remain to be selected. This
might deliver the benefits of the clique encoding for labelled graphs, while
avoiding the high memory cost and colouring time of encoding the full instance.

We believe there is more to be discovered about branching heuristics. There is
also the potential to branch on both sides, that is instead of branching on
vertices in $\V(G)$, it would be equally valid to branch on a vertex in
$\V(H)$, since our data structure treats the two graphs symmetrically. More
interestingly, we could choose which graph to branch on at each search node
using some heuristic (perhaps choosing based on whether the $P$ or $T$ set is
smaller), so long as we can ensure that the search remains complete.

It would be interesting to see whether these techniques are more broadly
applicable. Most obviously, we could solve the induced subgraph isomorphism
problem in the same way (and with nearly no changes to the code), but we could
not solve the non-induced version. However, we suspect that some other problems
may have a similar branching structure which would also benefit from a
different domain store representation.
